\documentclass[twoside,floatfix,a4wide]{revtex4}
\usepackage{multirow} % common packages
\usepackage{url}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{fancyhdr}
%\usepackage{asymptote}
%\usepackage{amsmath}
\usepackage{color}
\definecolor{mydarkred}{rgb}{0.7,0,0}
\newcommand{\checkme}[1] {\textcolor{mydarkred}{{\bf CHECK ME:}  \{#1\}}}
\newcommand{\comment}[1] {\textcolor{mydarkred}{\em  \{#1\}}} 

%\numberwithin{equation}{section} % Eguation numbering with section id. Reguires amsmath -package.
\pagestyle{fancy}
\fancyhead{} % clear all fields

\fancyhead[L]{\bf {Febuary 13, 2008}} % Left Odd, Right Even
\fancyfoot[L]{A.~Heikkinen {\em et al.}: 
{\em Ideal $\tau$ tagging with TMVA multivariate data-analysis toolkit}}

\fancyhead[R]{\thepage}
\fancyfoot[C]{} 
\newcommand{\urltilde}[1]{\texttt{#1}} % solves the tilde problem

\bibliographystyle{apsrev}

\hypersetup{
    bookmarks=true,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=true,      % page fit to window when opened
    pdftitle={My title},    % title
    pdfauthor={Author},     % author
    pdfsubject={Subject},   % subject of the document
    pdfnewwindow=true,      % links in new window
    pdfkeywords={keywords}, % list of keywords
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links
    citecolor=green,        % color of links to bibliography
    filecolor=blue,         % color of file links
    urlcolor=red            % color of external links
}

\begin{document}

\title{Ideal $\tau$ tagging with TMVA multivariate data-analysis toolkit
\footnote{Paper \cite{ah09bProceedings} in preparation for CHEP 2009, 21 - 27 March 2009 Prague, 
Czech Republic}}
%\url{http://www.particle.cz/conferences/chep2009/}}
%\title{A Geant4 physics list for spallation reactions}

\author{\underline{A.~Heikkinen}, P.~Kaitaniemi, V. Karim\"{a}ki,
 R.~Kinnunen,  M.~J.~Kortelainen, T.~Lamp\'{e}n, S.~Lehti, T.~Lind\'{e}n, and L.~Wendland} 
\affiliation{Helsinki Institute of Physics, P.O. Box 64, FIN-00014 University of Helsinki, Finland.
E-mail: aatos.heikkinen@cern.ch}

\begin{abstract}
We report our experience on using ROOT package TMVA for
multivariate data analysis, for a problem of $\tau$ tagging in the
framework of heavy charged MSSM Higgs boson searches at the LHC.
With a generator level analysis, 
we investigate how in the ideal case $\tau$ tagging could be performed and 
hadronic $\tau$ decays separated from the
hadronic jets of QCD multi-jet background present in LHC experiments. 
A successful separation of the Higgs signal from the background 
requires a rejection factor of $10^5$ or better against the QCD background. 
The $\tau$ tagging efficiency and background rejection are studied with various MVA classifiers.

%{\bf CHEP'07 abtract (see \cite{heikkinen07lProceedings}):}
%{\em We test the usage of a Toolkit for Multivariate Data Analysis (TMVA) in b tagging.
%Tagging b jets associated with heavy neutral MSSM Higgs bosons at the LHC can be used to
%extract the Higgs bosons from the Drell-Yan background, for which the associated jets are
%mainly light quark and gluon jets. Achievable b tagging effciency is studied with more than
%ten MVA classifiers at 1% mistagging rate. Most classifiers were found to perform better than
%the simple track counting 

\end{abstract}

\maketitle


\tableofcontents

\thispagestyle{fancy}

\section{INTRODUCTION \label{section:intro}}
We have previously tested TMVA software in b-tagging for the search of MSSM Higgs bosons 
at the LHC \cite{heikkinen07lProceedings}.
\section{MULTIVARIATE DATA ANALYSIS}
\subsection{TMVA methodology}


\section{DATA AND VARIABLES}
\subsection{Event generation}
%\subsection{Ideal case vs. detector effects}
% smearing
%\subsection{Discriminating variables}
\subsection{Variables used in a standard analysis }

In order to enable comparison between different MVA classifiers we prepared a standard
analyis using six variabled with fixed preselections cuts.

\begin{verbatim}
Variables:
// Default value found with rectangular cuts on CMSSW in parenthesis
// =================================================================
// jet energy (ET > 119 GeV)
jetEt
// jet eta (|eta| < 2.0)
jeteta
// tracker isolation: pT threhold for tracks to be ignored in isolation annulus
//   (trigger uses cone of 0.50, signal cone=0.04, default: max pT < 0.9 GeV/c)
log(isolMaxPt50)
// ECAL isolation: energy threshold for maximum energy in isolation annulus
//   (optimum isolation annulus 0.10-0.50, max ET < 1.9 GeV)
log(ecalIsolEt10_50)
// Rejection of electrons and neutral hadrons (K0's):
//   variable: ET^(HCAL_0-0.40)/pT^(track)-1, default: -0.98 < hcalRatio < 0.10
log(hcalRatio)
// tau helicity correlations (D.P.Roy, Phys.Lett.B459:607-614):
//   variable: Rtau = P(leading track) / E(jet), default: Rtau < 0.80
rtau
\end{verbatim}

Signal and background cuts:
\begin{verbatim}
signalTracks == 1
jetEt > 80
abs(jeteta) < 2.4
ldgPt > 20
\end{verbatim}


\subsection{IMPLEMENTATION \label{section:implementation}}
[code example]

[listing waht was coded, changed in TMVA]

\section{RESULTS} \label{sec:example}
\input{aatos} % NN
\input{pekka}
\input{veikko}
\input{ritva}
\input{matti}
\input{tapio}
\input{sami}
\input{tomas}
\input{lauri}

[Critics: TMVA bugs, is it already mature? Problems?]

[Praisal: what is now working compared to CHEP'07]

\section{CONCLUSION AND DISCUSSION} \label{sec:conclusion}
TMVA

%\begin{lstlisting}
%\end{lstlisting}

\bibliographystyle{unsrt}  % Options plain, unsrt, alpha, abbrv
%\bibliography{refs.bib} %10 p
\bibliography{chep09.bib} %10 p

\input{notes} % Misc. note for the project.
\end{document}
